Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
added 5.1 Description of the benchmarks

The table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from literature~\cite{Franklin15,converters,maglev,CTMS} and adopted in our experiments.

%The first plant represents a DC motor position model from~\cite{CTMS}. It is a third order system and presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%0		& 1 		& 0						\\
%0 		& -1.087	& 8587					\\
%0		& -9964		& -1.455\times 10^{6}	\\
%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
%0 \\ 0 \\ -1.455\times10^{6}
%\end{array}\right]
%$$
%%
%$$
%\textbf{C}=\left[\begin{array}{ccc}
%1 & 0 & 0\\
%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
%\theta \\ \dot{\theta} \\ i \\
%\end{array}\right],
%$$
%where the states $\theta$, $\dot{\theta}$, and $i$ are respectively the rotor angular position, rotor angular rate and the current of armature. The DC motor is stable in open loop.
%
%The second benchmark is an aircraft pitch dynamics model extracted from~\cite{CTMS}. It is a third order system and it presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.313	& 56.7 		& 0		\\
%-0.0139	& -0.426	& 0		\\
%0		& 56.7		& 0		\\
%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
%0.232 \\ 0.0203 \\ 0
%\end{array}\right]
%$$
%%
%$$
%\textbf{C}=\left[\begin{array}{ccc}
%0 & 0 & 1\\
%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
%\alpha \\ \dot{\theta} \\ \theta \\
%\end{array}\right],
%$$
%where the states $\alpha$, $\dot{\theta}$, and $\theta$ are respectively the aircraft attack angle, pitch rate and the pitch angle. The aircraft pitch dynamic is critically stable in open loop, with a pole in origin of $s$-plane.
%
%The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}. It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%0		& 1 		& 0		\\
%1752	& 0			& -34.07\\
%0		& 0			& -38.27\\
%\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
%0 \\ 0 \\ 1.923
%\end{array}\right]
%$$
%%
%$$
%\textbf{C}=\left[\begin{array}{ccc}
%1 & 0 & 0\\
%\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
%z \\ \dot{z} \\ i \\
%\end{array}\right],
%$$
%where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
%
%There are three benchmarks representing classic DC-DC converters: buck, boost, and buck-boost. They are SISO second-order systems stable in open-loop, and their state vector is $\textbf{x}=\textbf{x}=\left[\begin{array}{c}
%i_{L} \\ v_{C}\\
%\end{array}\right]$, where $i_{L}$ is the current in the coil and $v_{c}$ is the voltage on the capacitor. The matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, and $\textbf{D}$ for the buck converter are:
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& -500 \\
%4545	& -1515\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%125 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 1\\
%\end{array}\right],~ \textbf{D}= 0.
%$$
%
%The matrices of the boost converter are:
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& -375 \\
%3409	& -1515\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%500 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 1\\
%\end{array}\right],~ \textbf{D}= 0.
%$$
%
%Finally, the matrices of the buck-boost converter are:
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& 375 \\
%-3409	& -1515\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%125 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 1\\
%\end{array}\right],~ \textbf{D}= 0.
%$$
%
%Additionally, various dynamic systems model were extracted from~\cite{Franklin15} and incorporated to our test suite. They are: 
%\begin{itemize}
%\item{\textbf{automotive cruise control system:} 
%$$
%\textbf{A}=-0.05,~ \textbf{B} = 0.03125~
%\textbf{C}=0.032,~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{DC motor:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%-1000		& -13 \\
%-8			& 0\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%4 \\ 0 \\
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0 & 6.25\\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{helicopter longitudinal motion:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.42		& 0.0168		& -0.396	\\
%0.5			& 0				& 0			\\
%0			& 0.5 			& 0			
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%16 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%0.6125	& -0.6125	& 15.44 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{inverted pendulum cart position:} 
%$$
%\textbf{A}=\left[\begin{array}{cccc}
%0		& 1		& 0 	& 0	\\
%1		& 0		& 0		& 0	\\
%0		& 1 	& 0		& 0 \\
%0		& 0		& 1 	& 0 \\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cccc}
%0	& 0	& 1 & -0.75 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{inverted pendulum angle:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& 1	\\
%1		& 0	\\
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
% 0	& 1 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{magnetic pointer:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.271		& -0.05336	& 0	\\
%0.03125		& 0			& 0	\\
%0			& 0.01562 	& 0	\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%0	& -0.5888	& -0.2562 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{magnetic suspension:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& 31.25	\\
%32		& 0		\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%8 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%0	& 9.766 	\\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{pendulum:} 
%$$
%\textbf{A}=\left[\begin{array}{cc}
%0		& -2.453	\\
%4		& 0			\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%4 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cc}
%-1.225	& -2.15 	\\
%\end{array}\right],~ \textbf{D}= 9.8;
%$$
%}
%\item{\textbf{1/4 car suspension:} 
%$$
%\textbf{A}=\left[\begin{array}{cccc}
%-516.1	& -222.1& -79.75& -33.06	\\
%256		& 0		& 0		& 0			\\
%0		& 64 	& 0		& 0 \\
%0		& 0		& 32 	& 0 \\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%8 \\ 0 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{cccc}
%0	& 0	& 9.969 & 4.133 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{computer tape driver:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-1760		& -976.6	& -457.8	\\
%1024		& 0			& 0			\\
%0			& 512 		& 0			\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%8 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%1.5	& 2.051	& 1.144 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\item{\textbf{USCG cutter Tampa heading angle:} 
%$$
%\textbf{A}=\left[\begin{array}{ccc}
%-0.271		& -0.05336	& 0	\\
%0.03125		& 0			& 0			\\
%0			& 0.01562 	& 0			\\	
%\end{array}\right],~ \textbf{B} = \left[\begin{array}{c}
%1 \\ 0 \\ 0
%\end{array}\right]~
%\textbf{C}=\left[\begin{array}{ccc}
%0	& -0.5888	& -0.2562 \\
%\end{array}\right],~ \textbf{D}= 0;
%$$
%}
%\end{itemize}

>>>>

Table~\ref{table:State-space benchmarks} summarizes the list of benchmarks extracted from the literature~\cite{Franklin15,maglev,converters,CTMS}. \textit{DC Motor Position} plant provides the rotary motion that coupled with wheels and cables provides translational motion. \textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and control based on the pitch dimension only. \textit{Ball Magnetic Levitation} plant describes the magnetic field that keeps a metal ball hanged in air.
